\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Your Paper}
\author{You, also you}

\begin{document}
\maketitle

\begin{abstract}
Your abstract.\\
You're*
\end{abstract}

\section{Doe lekkere layout ftenks}
The domains we chose are blocks and gripper.
%their properties, a global overview of the operators and objects in the domain. 

\subsection*{Blocks}
\subsubsection*{properties}
\begin{itemize}
\item[on x y $-$] A block x is on top of another block y.
\item[ontable x $-$] A block x is on a table.
\item[clear x $-$] Nothing is on top of block x
\item[handempty $-$] The hand is not holding anything.
\item[holding x $-$] The hand is holding a block x.
\end{itemize}
\subsubsection*{objects}
\begin{itemize}
\item [block $-$] A stackable block.
\item [table $-$] A table on which blocks can stand.
\item [hand $-$] A hand capable of picking up blocks.

\end{itemize}

\subsubsection*{operators}
\begin{itemize}
\item [pick-up x $-$] The hand picks up block x from the table.
\item [put-down x $-$] The hand puts down block x on the table.
\item [stack x y $-$] The hand puts down block x on a block y.
\item [unstack x y $-$] The hand picks up a block x that is on top of a block y.
\end{itemize}


\subsection*{Gripper}
\subsubsection*{properties}
\begin{itemize}
\item [room r $-$] r is a room.
\item [ball b $-$] b is a ball.
\item [gripper g $-$] g is a gripper.
\item[at b r $-$] A ball b is in room r.
\item[free g $-$] A gripper g is not holding anything.
\item[carry o g $-$] An object o is carried by a gripper g. 
\item[at-robby r $-$] Robby the robot is in a room r. %maar defuq is robby. Vgm is robby een obscure referentie naar een robot.

%\item [Rooms $-$] The domain consists of rooms which are either empty (free) or occupied (not free).
\end{itemize}
\subsubsection*{objects}
\begin{itemize}
\item [room] 
\item [ball]
\item [gripper $-$] A thing which can be used to pick up and drop objects.
\item[obj $-$] Any object that can be handled by a gripper.
\item[Robby $-$] A robot with two grippers which can move between rooms.
\end{itemize}
% @Niels:
% objects: room, ball, gripper 
% operators: move, pick, drop
% zoiets? Jaa denk het wel
\subsubsection*{operators}
\begin{itemize}
\item [move from to $-$] Robby the robot moves from room from to room to. 
\item [pick obj room gripper $-$] Robby the robot picks up obj ball with gripper gripper in room room.
\item [drop obj room gripper $-$] Robby the robot drops obj ball with gripper gripper in room room.
% This shit looks ridiculous. MOON MOON. Boaty mcBoatFace.


\end{itemize}
\end{document}